Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-10 Latex/journal_v1/V5/pr.tex
add code
add convergence

\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 }_{\text{(Quantization Noise)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service
\begin{equation}\label{eq2}
\textstyle y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}
%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization noise 
($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}
\end{split}
\end{equation}
Where $j \in \{2,3\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

Suppose the mean total delay is depicted as $T_{tot}$.

@@

T^{tot} &=  T^{proc} + T^{tr} + T^{pro}\\
T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF}\\
T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t}  \\
T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}  \\

@@

Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively.

@@

T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}}\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}\\

@@

In addition, $T_{u(s,i)}^{RU}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
 The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue.

@@

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall s, \forall r, \forall k\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

@@

@@

In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms. We consider three network slices, for eMBB, URLLC and mMtc services.
Assume we have six 4-antenna O-RU (MISO) located in a cell with a diameter of 500 meters. We consider 25 PRB in the network.

>>>>

\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(Quantization Noise)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

To obtain SNR as formulated in \eqref{eq1}, let $y_{u(s,i)} $ be the received signal of UE $i$ in $s^{th}$ service
\begin{equation}\label{eq2}
\textstyle y_{u(s,i)} = \sum_{r = 1}^{R}\sum_{k=1}^{K_s} \boldsymbol{h}^{H \: k}_{r,u(s,i)} g_{u(s,i)}^r e^k_{r,u(s,i)}\mathfrak{y}^k_{r,u(s,i)}+ z_{u(s,i)},
\end{equation}
%\boldsymbol{w}^k_{r,u(s,i)}p^k_{r,u(s,i)}
where $\mathfrak{y}^k_{r,u(s,i)} =\boldsymbol{w}^k_{r,u(s,i)}{p^{k \: \frac{1}{2}}_{r,u(s,i)}} x_{u(s,i)}+ \boldsymbol{q}_{r}$
and $ x_{u(s,i)}$ depicts the transmitted symbol vector of UE $i$ in $s^{th}$ set of service,  $z_{u(s,i)}$ is the additive Gaussian noise $z_{u(s,i)} \backsim \mathcal{N}(0,N_0)$ and $N_0$ is the noise power.
In addition, $\boldsymbol{q}_{r} \in \mathbb{C}^{J }  $ indicates the quantization Gaussian noise 
($\boldsymbol{q}_{r} \backsim \mathcal{N}(0,{\sigma_q}^2\boldsymbol{I_{R}} )$), which is made from signal compression in O-DU.

The achievable data rate for the $i^{th}$ UE request in the $s_{1}^{th}$ application of service type 1 (eMBB) can be written as $\mathcal{R}_{u(s_1,i)}$ that is formulated as below.
\begin{equation}\label{eq3}
\begin{split}
\mathcal{{R}}_{r,u(s_1,i)}^{k} &=  B \log_2({1+ \rho_{r,u(s_1,i)}^{k}}) ,\\
\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)}
\end{split}
\end{equation}
where $B$ is the bandwidth of system. 
$\mathcal{R}_{u(s_1,i)}^{r}$ is the achievable rate of each RU $r$ to UE $i$ in slice $s_1$.
Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th}$ ( $j \in \{2,3\}$) application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission, the achievable data rate is approximated from following \cite{setayesh2020joint},
\begin{equation}\label{eq11}
\begin{split}
\mathcal{{R}}_{r,u(s_j,i)}^{k} &= B \log_2({1+ \rho_{r,u(s_j,i)}^{k}} - \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k},\\
\mathcal{R}_{u(s_j,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_j,i)}^{r} g^r_{u(s_j,i)}.
\end{split}
\end{equation}
Where $j \in \{2,3\}$. Also we have
\begin{equation}\label{shortPacket}
 \zeta_{u(s_j,i)}^{k} = log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\mathfrak{C}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})
\end{equation}
Where, $\epsilon $ is the transmission probability, $Q^{-1}$ is the inverse of Q- function (Gaussian),
$\mathfrak{C}_{u(s_j,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_j,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_j$, experiencing PRB $k$ and
$N_{u(s_j,i)}^{k}$ represents the blocklength of it. 
$\mathcal{R}_{u(s_j,i)}^{e,r}$ is the achievable data rate that is transmitted by O-RU $r$ to UE $i$ requesting service $s_j$.

@@

Suppose the mean total delay is depicted as $T_{tot}$,

@@

T^{tot} &=  T^{proc} + T^{tr} + T^{pro},\\
T^{proc} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{mid,t} + T^{b,t},  \\
T^{pro} &= T^{fr,p} + T^{mid,p} + T^{b,p}.  \\

@@

Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},

@@

T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}}.\\

@@

In addition, $T_{u(s,i)}^{RU}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
 The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
an exponential distribution with mean $1/R_{u(s,i)}$ and can be modeled as a M/M/1 queue \cite{SystemCostMinimization,luong2018joint,luong2018novel}.

@@

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
Where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
Where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

\subsubsection{Complexity Order}

@@

\subsubsection{Convergence Analysis}
We can guarantee the convergence of the iterative algorithm if the objective function is the strictly ascending function concerning the number of iterations \cite{gholipoor2020resource}.
Consider the aggregate throughput as $\mathcal{T(\bold{P},\bold{E},\bold{G})} =\sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}}$. 
In the first step of the iteration i of the algorithm \ref{alg2} (IABV), we have $\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1})$.
In this step, optimal power and PRB allocation are obtained for the fixed O-RU association, so we have
$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
In the second step of the iteration i, the optimal O-RU association is achieved to maximize the aggregate throughput. So we have this inequality
$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
As a result, we have 
$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
Hence, in each step of the iteration, the aggregate throughput increased.
Note that $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*})$ is the achieved aggregate throughput 
for all the feasible resource allocation solutions of $\{\bold{P},\bold{E},\bold{G}\}$.
So, $\mathcal{T}^*(\bold{P}^{*},\bold{E}^*,\bold{G}^{*}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i})$ and thus in each iteration, the aggregate throughput can not be larger than the optimal solution.
So the the aggregate throughput is ascending function concerning the number of iterations and it will converge to the optimal solution.
In addition, if we assume that the interference is set to be zero ${I}_{r,u_{(s,i)}}^{k}=0$,
and we suppose that each UE has the maximum power $p_{r,u_{(s,i)}}^k = P_{s}^{max}$,
and we consider that all PRB is assigned to all UE $e_{r,u_{(s,i)}}^k = 1 \forall s,\forall i$
and each UE is assigned to the nearest O-RU with the best channel quality. So, the solution of this allocation, is the upper bound 
for the aggregate throughput. Thus,
we can guarantee the convergence of our iterative algorithm since the objective function $\mathcal{T}$ is the ascending function concerning the number of iterations
 and it has the upper bound.  

@@

In this section, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, URLLC, and mMtc services.
Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{cell.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{O-RU placement in a cell}
  \label{fig:cell}
\end{figure}
Here, The channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent.
Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
and it is the Rayleigh fading channel between the UE and O-RU.
We consider 25 PRBs are used in the network and the
packet size is equal to 20 bytes.
